Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-03-13 2019/NUMTA_Barkalov/SoftComputing/article.tex
correct some typos

\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{lineno,hyperref,amsmath}
\usepackage{multirow}
\usepackage[round]{natbib} 
\usepackage[misc]{ifsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

	Since we have assumed that $x'$ is a limit point for the IM-DL and  $x' \neq \bar x$, then there exists such a sequence of the intervals $[x_{t-1}, x_t], t=t(k)$ that $x' \in [x_{t-1}, x_t], R_{loc}(t)>0$, and $R_{loc}(t) \rightarrow 0$. This property of the characteristics of the intervals shrinking to the limit point has been established when proving the theorem on the convergence of the IA in \cite{Strongin2000}.

	Therefore, for large enough, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t)
\end{equation}
and (according to Rules 5 and 6 of the IA-DL method) the next iteration falls into the interval $[x_{j-1}, x_j]$, which contradicts our assumption regarding the non-limit nature of the point $\bar x$. The theorem is proven.

>>>>

\smartqed  % flush right qed marks, e.g. at end of proof
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{hyperref,amsmath}
\usepackage[pagewise]{lineno}
\usepackage{multirow}
\usepackage[round]{natbib} 
\usepackage[misc]{ifsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

%\linenumbers

@@

	Since we have assumed that $x'$ is a limit point for the IA-DL and  $x' \neq \bar x$, then there exists such a sequence of the intervals $[x_{t-1}, x_t], t=t(k)$ that $x' \in [x_{t-1}, x_t], R_{loc}(t)>0$, and $R_{loc}(t) \rightarrow 0$. This property of the characteristics of the intervals shrinking to the limit point has been established when proving the theorem on the convergence of the IA in \cite{Strongin2000}.

	Therefore, for large enough $k$, the following inequality will be true
\begin{equation}
	R_{glob}(j) > \rho R_{loc}(t)
\end{equation}
and (according to Rules 5 and 6 of the IA-DL method) the next iteration falls into the interval $[x_{j-1}, x_j]$, which contradicts our assumption regarding the non-limit nature of the point $\bar x$. The theorem is proven.
